\newcommand{\function}[4]{
  \textbf{#1} (\emph{#2}): #3 \newline
  \emph{\color{teal} #4}
}


\subsection{Design decisions}
\emph{Our interpretation of the task.} There are doctors and patients. The doctors are able to mint Vaccination Slot tokens. The doctors are able to burn \emph{(invalidate)} a token. The most important properties of a single token are: Type \emph{(of the vaccine)}, Date \emph{(when the token should be burned)}, Burned \emph{(is it used up)}, Previous \emph{(previous vaccine type the patient got)}.

A patient can hold only one non-burned token and unlimited number of burned. A patient cannot trade a burned token.


\subsection{Data model}
TokenId is generated as a Universal Unique Identifier. Type is actually an \emph{enum} and it can be any of the following:
\begin{itemize}
  \item Alpha
  \item Bravo
  \item Charlie
  \item Delta
  \item Echo
\end{itemize}

\begin{center}
  \begin{table}[!ht]
    \centering
    \begin{tabular}{|c | c | c | c |}
      \hline
      \multicolumn{4}{|c|}{Token}                                              \\
      \hline
      name     & type      & comment                   & implemented interface \\
      \hline
      TokenId  & string    & generated id of the token & erc721                \\
      Type     & string    & vaccine type (enum)       & vaccinationSlot       \\
      Date     & time.Time & vaccination date          & vaccinationSlot       \\
      Previous & string    & vaccine type (enum)       & vaccinationSlot       \\
      Owner    & string    & owner of the token        & erc721                \\
      Burned   & boolean   & is it used up             & erc721 optional       \\
      Approved & string    &                           & erc721                \\
      \hline
    \end{tabular}
    \caption{Vaccination Slot token's data model.}
  \end{table}
\end{center}


\begin{center}
  \begin{table}[!ht]
    \centering
    \begin{tabular}{| c | c |}
      \hline
      \multicolumn{2}{|c|}{Approval} \\
      \hline
      name     & type                \\
      \hline
      Owner    & string              \\
      Operator & string              \\
      Approved & bool                \\
      \hline
    \end{tabular}
    \caption{Approval object's data model.}
  \end{table}
\end{center}

\begin{center}
  \begin{table}[!ht]
    \centering
    \begin{tabular}{| c | c |}
      \hline
      \multicolumn{2}{|c|}{Transfer} \\
      \hline
      name    & type                 \\
      \hline
      From    & string               \\
      To      & string               \\
      TokenId & string               \\
      \hline
    \end{tabular}
    \caption{Transfer object's data model.}
  \end{table}
\end{center}

\newpage
\subsection{API}
Inherited from \href{https://eips.ethereum.org/EIPS/eip-721}{ERC-721 specification}, function names may differ. For more specific developer documentation \href{run:spec.pdf}{see generated godoc.}
\subsubsection{Callable functions}
\begin{itemize}
  \item \function{BalanceOf}{owner string}{int}{Number of tokens in owner's wallet}
  \item \function{OwnerOf}{tokenId string}{string}{Owner of token}
  \item \function{TransferFrom}{from string, to string, tokenId string}{bool}{Transfering a token from wallet A to wallet B (if successful). }
  \item \function{Approve}{operator string, tokenId string}{bool}{ Change or reaffirm the approved address for an NFT }
  \item \function{SetApprovalForAll}{operator string, approved bool}{bool}{  }
  \item \function{GetApproved}{tokenId string}{string}{  }
  \item \function{IsApprovedForAll}{owner string, operator string}{bool}{  }
  \item \function{ClientAccountId}{}{string}{  }
  \item \function{GetSlots}{owner string}{VaccinationSlot[]}{ returns an array of owner's slots }
  \item \function{IssueSlot}{vaccine string, date string, patient string}{string}{ Create's a slot (if client is authorized) and transfers to specific patient (wallet) }
\end{itemize}
\subsubsection{Non-callable functions}
\begin{itemize}
  \item \function{readVaccinationSlot}{tokenId string}{VaccinationSlot}{}
  \item \function{vaccinationSlotExists}{tokenId string}{bool}{}
\end{itemize}


\subsection{Implemention details}


\subsection{Test cases}